---
title       : The First Chapter
description : Insert the chapter description here


--- type:VideoExercise lang:r xp:50 skills:1
## Analyze movies

*** =video_link
//player.vimeo.com/video/154783078

--- type:MultipleChoiceExercise lang:r xp:50 skills:1
## A really bad movie

Have a look at the plot that showed up in the viewer to the right. Which type of movie has the worst rating assigned to it?

*** =instructions
- Adventure
- Action
- Animation
- Comedy

*** =hint
Have a look at the plot. Which color does the point with the lowest rating have?

*** =pre_exercise_code
```{r}
# The pre exercise code runs code to initialize the user's workspace. You can use it for several things:

# 1. Preload a dataset. The code below will read the csv that is stored at the URL's location.
# The movies variable will be available in the user's console.
movies <- read.csv("http://s3.amazonaws.com/assets.datacamp.com/course/introduction_to_r/movies.csv")

# 2. Pre-load packages, so that users don't have to do this manually.
library(ggplot2)

# 3. Create a plot in the viewer, that students can check out while reading the exercise
ggplot(movies, aes(x = runtime, y = rating, col = genre)) + geom_point()
```

*** =sct
```{r}
# The sct section defines the Submission Correctness Tests (SCTs) used to
# evaluate the student's response. All functions used here are defined in the 
# testwhat R package

msg_bad <- "That is not correct!"
msg_success <- "Exactly! There seems to be a very bad action movie in the dataset."

# Use test_mc() to grade multiple choice exercises. 
# Pass the correct option (Action, option 2 in the instructions) to correct.
# Pass the feedback messages, both positive and negative, to feedback_msgs in the appropriate order.
test_mc(correct = 2, feedback_msgs = c(msg_bad, msg_success, msg_bad, msg_bad)) 
```

--- type:NormalExercise lang:r xp:100 skills:1
## Basic Math

In this exercise, you will learn to do basic arithmetic in R. You can do addition, subtraction, multiplication, and division using the notation shown:

```
3 + 4
5 - 2
7 * 8
4 / 5
```

*** =instructions
- Add the values 5 and 3.
- Subtract 10 from 20.
- Multiply 10 by 67.
- Divide 25 by 5.

*** =hint
Refer to the examples above.

*** =pre_exercise_code
```{r}

```

*** =sample_code
```{r}
# Define v as a vector containing 1, 2, and 3


# Find missing values: missing


# Print missing to the console


```

*** =solution
```{r}
# Define v as a vector containing 1, 2, and 3
v <- c(1, 2, 3)

# Find missing values: missing
missing <- is.na(v)

# Print missing to the console
missing

```

*** =sct
```{r}
test_correct({test_object("missing")}, 
             {
               test_function("is.na", args = "x")
               test_error()
             })

# Final message the student will see upon completing the exercise
success_msg("Good work!")
```
